---
title: ""
author: ""
date: ""
output: html_document
---

# 1. Use the `penguins` dataframe and create your own `base_graph`. Make sure to have a continuous variable on the y-axis and a categorical variable on the x-axis.

```{r}

```

# 2. Modify your `base_graph` so the scale is more appropriate and represents the full range.

```{r}

```

# 3. Modify your `base_graph` so the padding is gone.

```{r}

```

# 4. Modify your `base_graph` so that it has more appropriate titles for the y- and x-axis. Additionally, add an appropriate title, subtitle (if needed), figure tag, and caption.

```{r}

```

# 5. Create a new variable called `modified_graph` that takes your `base_graph` and saves all modifications you've added thus far. Then, try applying some different themes to your `modified_graph`.

```{r}

```

# 6. Add some code to `modified_graph` to modify your visualization's titles and increase their legibility.

```{r}

```

# 7. Add some code to `modified_graph` to modify your visualization's caption and increase its legibility.

```{r}

```

# 8. Add some code to `modified_graph` to modify your visualization's axes titles and increase their legibility.

```{r}

```

# 9. Add some code to `modified_graph` to modify your visualization's axes values and increase their legibility.

```{r}

```

# 10. Use the code you've generated throughout the previous few examples to create a new default theme setting.

```{r}

```


# 11. Use patchwork to combine your `base_graph` and `modified_graph` to compare the two. Try arranging them in different layouts using different operators.

```{r}

```

