---
title: ""
author: ""
date: ""
output: html_document
---

# 1. Practice changing the values for the 3 arguments in `scale_*_hue()` and see how they affect your visualization. Change multiple simultaneously and see how combinations work!

```{r}

```

# 2. Change the colors in both graphs to manually set values. Find a combination of colors you think work well together and are perceptually uniform.

```{r}

```

# 3. Create 2 single hue gradients that you think seem perceptually uniform. Then create 2 multiple-hue gradients (using either function to do so) that you think seem perceptually uniform.

```{r}

```

# 4. Create 2 visualizations using divergent scales that you think are equally uniform in both directions from the midpoint.

```{r}

```

# 5. Try out some different palettes from RColorBrewer, pick your top 3, and modify your visualizations from above to use those palettes.

```{r}

```

# 6. Take your code from Exercise 5 and replace the color palettes from RColorBrewer with ones from viris.

```{r}

```


