---
title: ""
author: ""
date: ""
output: html_document
---

# Set up
```{r}
library(tidyverse)
msleep2 = msleep %>%
  select(-conservation)
```

# 1. Use helper functions to...
##  A. Select all columns that start with "sleep".
##  B. Select all columns that end with "wt".

```{r}

```

# 2. Select all columns that contain "re".

```{r}

```

# 3. Use `where()` to select...
##  A. All columns that are numeric.
##  B. All columns that are characters.

```{r}

```

# 4. User helper functions to select the columns that...
##  A. Contain "re" and are *numeric* data.
##  B. End with "e" and do not start with "sleep".

```{r}

```

# 5. 
##  A. Filter for observations where scores in any variable that ends with "wt" is above 35.
##  B. Filter for observations where scores in any variable that starts with "sleep" is less than 2.

```{r}

```

# 6. Use helper functions to...
##  A. Round all the columns that are *numeric*.
##  B. Round only the columns that are *numeric* and start with "sleep".
##  C. `scale()` the columns that end with "wt" and are *numeric*, then filter the results for only those where all columns that end with "wt" are greater than 0.

```{r}

```


