---
title: ""
author: ""
date: ""
output: html_document
---

```{r}

```


# 1. 
##  A. define a variable `z` that will randomly sample a value from `1:100`.<br>

##  B. Write an `if` statement that will `print()` "My first R if" if `z` is less than 20. Run all the code in the cell.<br>

##  C. Add an `else` condition to your `if` statement that will print, "Still my first R if, but z is not less than 20." Run all the code in the cell.<br>

##  D. Between your `if` and `else` conditions, add an `else if` that will print "The else if evaluated TRUE!" when z is greater than 40 but less than 80. Run all the code in the cell.<br>

##  E. Try running all the code in the cell and see how often each string gets printed.

```{r}

```

# 2. Reformat your code from Exercise 1 to use the `ifelse()`

```{r}

```

# 3. Reformat your code from Exercise 1 to use the `case_when()`

```{r}

```

# 4. Use a `for` loop to to subtract 2 from all values in vector `v`.

```{r}
v = c(19, 22, 30, 23, 15, 22, 24, 19, 30, 23)
```

# 5.
##  A. Use a `for` loop to give a 1.5x bonus only to the employees in dataframe `work_df` who worked overtime.
##  B. Rewrite your code using `ifelse()` syntax to accomplish the same goal.

```{r}
work_df = data.frame("Name" = c("Jim", "Jo", "Jack", "Jana"),
                     "Pay" = c(80, 120, 100, 150),
                     "Overtime" = c(0,1,0,1))
```

# 6.   
##  A. Use `glimpse()` to exam the `msleep` dataset.<br>
##  B. What information have you learned about this dataset from the output?

```{r}

```

# 7. 
##  A. Use `head()` to exam the `msleep` dataset.
##  B. Modify your `head()` call to look at the first 7 rows of data.
  
```{r}

```







