---
title: ""
author: ""
date: ""
output: html_document
---

# Set up
```{r}
library(tidyverse)
msleep2 = msleep %>%
  select(-conservation)
```


# 1. 
##  A. Use `arrange()` to order the `msleep2` dataset by `bodywt`.
##  B. Modify your `arrange()` call to order the `bodywt` column from greatest to least.
##  C. What is the largest animal recorded in this dataset?

```{r}

```

# 2. Both of the weight columns in this dataset are measuring in kilograms. Use `rename()` to give those variables more informative names.

```{r}

```

# 3.
##  A. Move the `order` column to be positioned before the `vore` column.
##  B. Move the `sleep_total` column to be positioned after the `sleep_cycle` column.
##  C. Move both wt columns to be positioned after `genus`.

```{r}

```

# 4.
##  A. Subset the `name` and `vore` columns.
##  B. Subset the `genus` and `order` columns.
##  C. Subset all the sleep related columns.

```{r}

```

# 5.
##  A. Use `select()` to get rid of the `awake` column.
##  B. Get rid of all columns related to the animal's weight.

```{r}

```

# 6. Filter the data to show only the observations where...
##  A. The animals are of Rodentia order.
##  B. The animals have a body weight of 5 or greater.
##  C. The animals are not herbivores.

```{r}

```


# 7. Filter the data to show...
##  A. The animals who sleep for over 14 hours total and weigh less than 3
##  B. The carnivores who spend over 10 hours awake, then subset only the `awake`, `vore`, and `sleep_total` columns.
##  C. All animals with a brain weight greater than 0.1 or spend less than 1 hour in rem, **except those who are herbivores**, then subset only the `brainwt`, `sleep_rem`, and `name` columns, and arrange the results by `awake` from greatest to least.

```{r}

```

# 8.   Filter the data to show...
##  A. Animals in the "Cetacea", "Cingulata", or "Pilosa" order, who sleep for a total of anywhere between 5 and 10 hours.
##  B. Modify the code from above to show only the `name`, `order`, `sleep_total`, and `brainwt`.
##  C. Modify the code from above to arrange by brain weight from least to greatest.

```{r}

```

# 9. Filter the data to show...
##  A. The animals who sleep for over 14 hours total and weigh less than 3.
##  B. The carnivores who spend over 10 hours awake, then subset only the `awake`, `vore`, and `sleep_total` columns.
##  C. All animals with a brain weight greater than 0.1 or spend less than 1 hour in rem, **except those who are herbivores**, then subset only the `brainwt`, `sleep_rem`, and `name` columns, and arrange the results by `awake` from greatest to least.

```{r}

```

# 10. 
##  A. Index the `sleep_total` variable from `msleep2`.
##  B. Find the mean of `sleep_total`.
##  C. Subset the data to only include carnivores, index the `bodywt` column, and find the average value. Do the same for herbivores. Which has a higher average body weight?

```{r}

```

# 11.
##  A. Subset the data for primates who spend more than 13 hours awake, arrange the `awake` column from greatest to least, index it, and the 2nd value from the resulting vector.
##  B. Using a process similar to the one above, write some code that will result in the value for the 2nd lowest brain weight for omnivores who spend less than 2 hours in rem.

```{r}

```

# 12. 
##  A. The unique values in the `vore` column.
##  B. The *number* of unique values in the `vore` column.

```{r}

```

# 13. 
##  A. The sleep variables are all measured in hours. Create a new variable called `sleep_total_m` that measures total **minutes** of sleep.
##  B. Create a new variable that represents the proportion of total sleep spent in rem, move that column to come after `sleep_rem`, filter to show only observations with a ratio of 0.25 or greater, arrange the new column from greatest to least, and index the `bodywt` of the animal with the highest ratio.

```{r}

```

# 14. 
##  A. Find out what the average total sleep is for all animals, then use `case_when()` to create a new column that has the value "sleepyhead" if the animal has a `sleep_total` higher than average, "wide-awake" if lower than average, and "average" if exactly average.
##  B. Use `ifelse()` to create a new column just indicating whether the animal had a "higher" or "lower" `sleep_total` than average.

```{r}

```

# 15. 
##  A. Use `drop_na()` to remove all observations with an `NA`.
##  B. Only get rid of observations with an `NA` for `brainwt`.

```{r}

```

# 16. 
##  A. As mentioned above, the weight columns are measured in kg. Change these columns so that they contain the weight in lbs (1kg = ~2.205 lbs). Arrange the new body weight column from least to greatest, and index the value for the lightest animal in the dataset.
##  B. Change the `vore` column to be a *factor* instead of *character*, and the `awake` column to be a *character* instead of *numeric*.

```{r}

```

# 17. Take 3-4 visualizations you created in the exercises from the data visualization lectures and reorder the factor levels so they are in a more sensible order.

```{r}

```




