---
title: ""
author: ""
date: ""
output: html_document
---

# 1. Install the packages listed below:

- tidyverse
- patchwork
- magrittr
- viridis
- RColorBrewer
- DT
- ggExtra
- gridExtra
- reprex
- knitr
- markdown
- palmerpenguins
- janitor
- ggridges

# 2. Rewrite the following code as properly formatted pipe chains.

```{r exercise 2}
park(drive(start_car(find("keys")), to = "campus"))

pull(swoop(loop(laces)))

brush(tooth_paste(running_water(tooth_brush)), teeth)

leave_house(get_dressed(get_out_of_bed(wake_up(me))))
```


# 3. Download the files for today's class that came with the assignment and move them into your project directory we created last time. Using `here()` import both the .csv and .RData files. Make sure you save them to variables! Copy/paste their file path in the cell below.

```{r exercise 3}

```

# 4. Open up your exercises from the 3rd class. Export your dataframe as a .csv file called "my_dataframe.csv". Export your dataframe and all the variables you saved to an .RData file called "my_data.RData".

```{r exercise 4}

```


