---
title: ""
author: ""
date: ""
output: html_document
---

# Set up
```{r}
library(tidyverse)
msleep2 = msleep %>%
  select(-conservation)
```

# 1. Write some code to find the number of instances of each unique value of `vore`.

```{r}

```

# 2. Modify your code from exercise 1 to show the proportions, and verify that they sum to 1.

```{r}

```

# 3. Use `summarize()` to find the average number of hours each animal spends awake and the average brain weight. If there are any issues with missing values, modify your code to account for this.

```{r}

```

# 4. Modify your code from exercise 3 to show averages for each level of `vore`.

```{r}

```

# 5. 
##  A. Find the average of all variables that start with "sleep" for every level of `vore`.
##  B. Find the average and sd for all variables that end in "wt" for every level of `vore`.
##  C. Find the number of unique values for each variable that is a *character*.

```{r}

```

# 6. Take your code from Exercise 5 and replace the color palettes from RColorBrewer with ones from viris.

```{r}

```


